Volunteers in the Clouds: A Web Based Architecture to Harness Volunteer Resources for Low Cost Distributed Evolutionary Computation

### 2015-12-17 special-issue-ci/Response to reviewers-r2.tex

In the next sections you can find these comments and our responses
to them, along with the changes done.\\

\noindent
Yours sincerely,\\
The authors.

%-----------------------------------------------------------------------------
\section{Response to Editors}

\begin{quote}
\textbf{1) Be careful with the use of acronyms. They must be defined
  the first time appearing in the text. Moreover, the use of too many
  acronyms jeopardizes readability of the manuscript. Please, keep
  only those acronyms which are really needed.\\}
\end{quote}

All acronyms have been checked and defined in the first occurrence,
some unnecessary ones (like JS for JavaScript) eliminated.

\begin{quote}
\textbf{
2) NodIO-W2 is not presented in the abstract.\\
}

We have now made a small introduction to it.

\begin{quote}
\textbf{
3) Check the use of system vs framework.

We recommend to use only one of these two words all along the text.\\
}

In general, we have opted for framework, since it is a client-server
framework and it is more precise than {\em system}

\begin{quote}
\textbf{4) Considering only one subsection inside a section makes harder the paper comprehensibility.
For instance, in case of section IV, we recommend removing the caption
related to subsection A and keeping everything in just one section.\\}

Done. Thanks for the suggestion.

\begin{quote}
\textbf{ 5) We suggest re-writing the title of section IV as ``Baseline Experiments''.\\
6) We suggest re-writing the title of section V as ``Enhancing NodIO
with a web worker-based architecture''\\}

Done again and thanks.

\begin{quote}
\textbf{7) Section V should be split into two sections.
The new section may be entitled as ``Experimental trials'' and it should start at ``The experiments were run in the same way as before...''
Moreover, it would be better to remove the caption of subsetion V.A.
In case you think the section is too long then you may organize it
into two subsections (A. Setup and B. Results)\\}

If we understood it correctly, you thought that the section was too
long for a single {\em segment} and you wanted two subsections (not
two different {\em entities} of the same kind. This is what we have
done: introduced two subsections, one focused in the experiment we
presented on the first version, another on the experiment that
has been introduced in this version and entitled {\bf Tests with a
  floating-point hard optimization problem}. Thanks for the
suggestion, it is now much clearer.

\begin{quote}
\textbf{8) Minor typos.\\}

Fixed

\begin{quote}
\textbf{9) The following recent reference is closely related to your paper and it should be cited:
J. Alcala-Fdez and Jose M. Alonso, A survey of fuzzy systems software: Taxonomy, current research trends and prospects, IEEE Transactions on Fuzzy Systems, 2015. Doi:10.1109/TFUZZ.2015.2426212}
\end{quote}

Added.

### 2015-12-17 special-issue-ci/Response to reviewers-r2.tex

\begin{quote}
\textbf{9) The following recent reference is closely related to your paper and it should be cited:
J. Alcala-Fdez and Jose M. Alonso, A survey of fuzzy systems software: Taxonomy, current research trends and prospects, IEEE Transactions on Fuzzy Systems, 2015. Doi:10.1109/TFUZZ.2015.2426212}
\end{quote}

Added.

%-----------------------------------------------------------------------------
\section{Response to Reviewer \#1}

\begin{quote}
\textbf{I'm not, however, fully convinced about that the new experiment of solving Rastrigin's function be representative of a real world problem. The presented work, as is, has interesting merits, but the question of its usefulness remains uncertain if it would be used to solve a non-academic optimization problem. As the authors point out, reasonable performance is not ensured and their proposal could result in a pointless academic exercise.\\
After reading the revised paper, an arising question is why the
authors have used in Section IV a problem that is solved in around 1
second. An approach to simulate a hard problem could be to
artificially increase the evaluation time (e.g, by adding an idle
loop); this way, the problem would remain the same and the computing
time could be adjusted to try to gain some speed-up with the proposed
platform.\\}

This is an useful suggestion. We will try to add that kind of
experiment in the future. In fact, some of our previous papers have
used a similar technique successfully.

\begin{quote}
\textbf{Minor comments:
- The paper structure should be enhanced: there are subsections IV.A and V.A but there are not
IV.B nor V.B.}

As a response to editor's requests, this has been done.

\begin{quote}
\textbf{- In the first paragraph of Section V is said: ``! to perform the fifty runs'', but none is said before
about those fifty runs.}

It is mentioned now at the beginning of the paragraph

\begin{quote}
\textbf{- Figures should be improved: Fig.2 has huge fonts (and the caption should include the time unit),
while others Fig.3, Fig.4, etc include very small fonts.}

Fonts have been made more readable and uniform, and axis labeled.

\begin{quote}
\textbf{- The second version of the systems is named NodIO-W2 in Section V, but it is referred as to
NodIO2 in the conclusions.}
\end{quote}

It is called the same way now. Thanks a lot for your suggestions, and
we expect these changes satisfactory.

### 2015-12-17 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Finished response to eds refs #81
Continuing with rev1, refs #81

\begin{figure}[!t]
\centering
\includegraphics[width=12cm]{baseline-times.png}
\caption{Comparison of times to solution (labeled as {\bf times}) for the baseline system, using a {\tt
    Node.js} client, for different population sizes. Only
runs in which solution has been found are used for this graph.}
% Plotted with: ~/Code/splash-volunteer/data/plot-baseline.R
\label{fig:baseline}
\end{figure}
First, we establish the baseline performance by running fifty runs of the
evolutionary algorithm in a desktop client written using {\sf NodEO}
\cite{nodeo2014}, the basic JavaScript library we have used as base to
build {\sf NodIO}, the framework. This experiment tries to 
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$ and a population size equal to 512. The algorithm in a
single island was run until the solution (a string with all
ones) was found or five million evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform the fifty runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with a success rate upgraded to 100\% and an {\em average} duration of $3.46$
seconds. Results for these two experiments
are shown in Figure \ref{fig:baseline}. The baseline hardware system has these
characteristics: 
\begin{verbatim}
Linux penny 3.13.0-34-generic #60-Ubuntu SMP Wed Aug 13 15:45:27 UTC
2014 x86_64 x86_64 x86_64 GNU/Linux
\end{verbatim}
with a 4-core {\tt Intel(R) Core(TM) i7-4770 CPU @ 3.40GHz}.

@@

\subsection{Tests with floating-point hard optimization problems}

>>>>

\begin{figure}[!t]
\centering
\includegraphics[width=10cm]{baseline-times.png}
\caption{Comparison of times to solution (labeled as {\bf times}) for the baseline system, using a {\tt
    Node.js} client, for different population sizes. Only
runs in which solution has been found are used for this graph.}
% Plotted with: ~/Code/splash-volunteer/data/plot-baseline.R
\label{fig:baseline}
\end{figure}
First, we establish the baseline performance by running fifty runs of the
evolutionary algorithm in a desktop client written using {\sf NodEO}
\cite{nodeo2014}, the basic JavaScript library we have used as base to
build {\sf NodIO}, the framework. This experiment tries to 
find the solution to the 40-trap function with parameters $l=4, a=1,
b=2, z=3$ and a population size equal to 512. The algorithm in a
single island was run until the solution (a string with all
ones) was found or five million evaluations had been performed. It
took around a minute, on average, that is $68.9694$ seconds, to
perform these runs. In this experiment only 33, that is, 66\% were
successful. The experiments were repeated for population $p=1024$,
with a success rate upgraded to 100\% and an {\em average} duration of $3.46$
seconds. Results for these two experiments
are shown in Figure \ref{fig:baseline}. The baseline hardware system has these
characteristics: 
\begin{verbatim}
Linux penny 3.13.0-34-generic #60-Ubuntu SMP Wed Aug 13 15:45:27 UTC
2014 x86_64 x86_64 x86_64 GNU/Linux
\end{verbatim}
with a 4-core {\tt Intel(R) Core(TM) i7-4770 CPU @ 3.40GHz}.

@@

\subsection{Tests with a floating-point hard optimization problem}
